Mistriage

### 2019-05-17 ManuscriptMarkdown.Rmd
Rename ResultsMarkdown.Rmd to ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

---
title: "Mistriage"
author: "Martin Henriksson"
date: "190429"
output: word_document
---

@@

Table 2 shows model validation performance. Model validation performance refers to the model performance when applied in the validation subsample from the sample in which it was developed. The sample with the best validation model performance was the `r best.validation$Sample.name` sample with a median mistriage rate of `r best.validation$Validation.mistriage.median`. Performance in terms of under and overtriage for the same model was `r best.validation$Validation.undertriage.median`, and `r best.validation$Validation.overtriage.median`. Model validation performance varied across all samples with a median mistriage rate range of `r min(results$original.stats$Validation.mistriage.median)` - `r max(results$original.stats$Validation.mistriage.median)`. Uncertainty interval(UI) for validation mistriage, undertriage and overtriage ranged from 0 to 0.830 across all samples.

@@

# Discussion (Needs update with code snippets) 
This study aimed to assess how transfers of clinical prediction models for early trauma care between different contexts within a single health system affect mistriage rates. The most notable effects on model performance following model transfer compared to the original sample model was seen when the metropolitan model was transferred to the non-metropolitan sample. The performance of the metropolitan model transferred to the non-metropolitan sample was a mistriage rate of 0,51, and the validation mistriage rate of the non-metropolitan model was 0,20. This indicates that the mistriage increased by 0,31 when using the metropolitan model in a non-metropolitan setting. Mainly contributing to this increase in mistriage was the marked increase in overtriage when performing this model transfer. The UI of this difference however ranged from -0.055 to 0.630, indicating that our findings are compatible with a -0.055 decrease to 0.630 increase in mistriage. This means that with the negative UI (-0.055), the effect of transfer would be an improvement in model performance. The upper limit of the UI (0.630) would mean a marked decrease in model performance, especially compared to the point estimate of 0.31.

@@

## Conclusion (Needs update with code snippets) 
A clinical prediction model developed using logistic regression and GCS, RR and SBP as predictors can be used to predict 30-day mortality in different settings. Model transfer in the metropolitan and non-metropolitan data set lead to increased mistriage rate (95% UI -0.055 - 0.630). This was mainly due to a marked increase in overtriage. In all samples, 95% UI for model transfer comparison included 0. Poor model transfer can potentially lead to increased patient mortality and a misappropriation of resources. We recognize the limitations of this study, but believe further studies are warranted due to the potentially severe patient consequences.

>>>>

---
title: "Mistriage"
author: "Martin Henriksson"
date: "190517"
output: word_document
---

@@

Table 2 shows model validation performance. Model validation performance refers to the model performance when applied in the validation subsample from the sample in which it was developed. The sample with the best validation model performance was the `r best.validation$Sample.name` sample with a median mistriage rate of `r best.validation$Validation.mistriage.median`. Performance in terms of under and overtriage for the same model was `r best.validation$Validation.undertriage.median`, and `r best.validation$Validation.overtriage.median`. Model validation performance varied across all samples with a median mistriage rate range of `r min(results$original.stats$Validation.mistriage.median)` - `r max(results$original.stats$Validation.mistriage.median)`. Uncertainty interval(UI) for validation mistriage, undertriage and overtriage ranged from ... to ... across all samples.

@@

# Discussion (Needs update with code snippets) 
This study aimed to assess how transfers of clinical prediction models for early trauma care between different contexts within a single health system affect mistriage rates. The most notable effects on model performance following model transfer compared to the original sample model was seen when the metropolitan model was transferred to the non-metropolitan sample. The performance of the metropolitan model transferred to the non-metropolitan sample was a mistriage rate of ..., and the validation mistriage rate of the non-metropolitan model was .... This indicates that the mistriage increased by ... when using the metropolitan model in a non-metropolitan setting. Mainly contributing to this increase in mistriage was the marked increase in overtriage when performing this model transfer. The UI of this difference however ranged from ... to ..., indicating that our findings are compatible with a ... decrease to ... increase in mistriage. This means that with the negative UI (...), the effect of transfer would be an improvement in model performance. The upper limit of the UI (...) would mean a marked decrease in model performance, especially compared to the point estimate of ....

@@

## Conclusion (Needs update with code snippets) 
A clinical prediction model developed using logistic regression and GCS, RR and SBP as predictors can be used to predict 30-day mortality in different settings. Model transfer in the metropolitan and non-metropolitan data set lead to ... mistriage rate (95% UI ...). This was mainly due to .... In all samples, 95% UI for model transfer comparison included 0. Poor model transfer can potentially lead to increased patient mortality and a misappropriation of resources. We recognize the limitations of this study, but believe further studies are warranted due to the potentially severe patient consequences.
